---
title: "`r paste0('Libraries Programmes and Events: ', params$outcome, ' Outcome Analysis (', params$month, ' ', params$year, ')')`"
author: "`r paste0('Lee Durbin and ', params$outcome_owner)`"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
params:
  year: 2021
  month: July
  outcome: "Literacy"
  outcome_owner: "Kirstin Kane"
  outcome_url: https://aklcouncil.sharepoint.com/sites/tools-to-do-my-job/SitePages/Literacy-@-Auckland-Libraries.aspx
---


```{r setup, include=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## Overview

```{r overview}
source("data_prep.R")

# How many sessions were entered into the form?
monthly_submissions <- joined_data %>% 
  filter(month(as_date(delivery_datetime), label = TRUE, abbr = FALSE) == params$month & year(as_date(delivery_datetime)) == params$year) %>% 
  distinct(id) %>% 
  nrow()

# Of these, how many delivered against an outcome?
outcome_submissions <- joined_data %>% 
  filter(!is.na(outcome) & month(as_date(delivery_datetime), label = TRUE, abbr = FALSE) == params$month & year(as_date(delivery_datetime)) == params$year) %>% 
  distinct(id) %>% 
  nrow()

# Filter down to an outcome area
outcome_data <- joined_data %>% 
  filter(month(as_date(delivery_datetime), label = TRUE, abbr = FALSE) == params$month & year(as_date(delivery_datetime)) == params$year & outcome == params$outcome)

# Stats for sessions that delivered against a given outcome area
this_outcome <- outcome_data %>% 
  distinct(id, outcome, .keep_all = TRUE) %>% 
  summarise_data(outcome)
```

In `r params$month` `r params$year`, **`r prettyNum(monthly_submissions, big.mark = ",")`** in-scope programmes, events, and Book a Librarian sessions were delivered across Tāmaki Makaurau. You can browse through the complete dataset by downloading the [Data Explorer](`r params$outcome_url`).

Of these `r prettyNum(monthly_submissions, big.mark = ",")` activities, a total of **`r prettyNum(outcome_submissions, big.mark = ",")`** were reported as having delivered against one of the six outcome areas. In other words, **`r round((outcome_submissions/monthly_submissions)*100)`%** of the in-scope libraries activities delivered in `r params$month` `r params$year` were reported as having delivered against at least one of the six outcomes.

Of the `r prettyNum(monthly_submissions, big.mark = ",")` activities that were delivered in `r params$month` `r params$year`, **`r prettyNum(this_outcome$sessions, big.mark = ",")`** were said to have delivered against the [`r params$outcome` outcome](https://aklcouncil.sharepoint.com/sites/tools-to-do-my-job/SitePages/Literacy-@-Auckland-Libraries.aspx). In other words, **`r round((this_outcome$sessions/monthly_submissions)*100)`%** of the in-scope libraries activities delivered in `r params$month` `r params$year` were reported as having delivered against the Literacy outcome.

Looking specifically at the activities in `r params$month` `r params$year` that were said to have delivered against the `r params$outcome` outcome, **`r prettyNum(this_outcome$participants_adult, big.mark = ",")` adults** and **`r prettyNum(this_outcome$participants_children, big.mark = ",")` children** attended these sessions.

In `r params$month` `r params$year`, **`r prettyNum(this_outcome$duration, big.mark = ",")` hours** were devoted to activities that were said to have delivered against the `r params$outcome` outcome.
